### 2023-10-17 README.Rmd
update readme

# bayesinfmatcultphylo

@@

> Ben Marwick [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0001-7879-4531 ), David N. Matzig [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0001-7349-5401)   , Felix Riede [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0002-4879-7157), (2023). _`r Title`_.  <https://doi.org/xxx/xxx>

@@

> Ben Marwick [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0001-7879-4531 ), David N. Matzig [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0001-7349-5401)   , Felix Riede [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0002-4879-7157), (2023). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

> Ben Marwick [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0001-7879-4531 ), David N. Matzig [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0001-7349-5401)   , Felix Riede [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0002-4879-7157), (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

  - [:file\_folder: paper](/analysis/paper): Quarto source document
    for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis. It also has a rendered version,
    `paper.docx`, suitable for reading (the code is replaced by figures
    and tables in this file)
  - [:file\_folder: data](/analysis/data): Data used in the analysis.
  - [:file\_folder: figures](/analysis/figures): Plots and other
    illustrations
  - [:file\_folder:
    supplementary-materials](/analysis/supplementary-materials):
    Supplementary materials including notes and other documents
    prepared and collected during the analysis.

>>>>

# Bayesian inference of material culture phylogenies using continuous traits: A birth–death model for Late Neolithic/Early Bronze Age arrowheads from Northwestern Europe

@@

> Ben Marwick [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0001-7879-4531 ), David N. Matzig [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0001-7349-5401)   , Felix Riede [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0002-4879-7157), (2023). _`r Title`_.

@@

> Ben Marwick [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0001-7879-4531 ), David N. Matzig [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0001-7349-5401)   , Felix Riede [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0002-4879-7157), (2023). _`r Title`_. SocArXiv, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://osf.io/preprints/socarxiv/j2kva>

@@

> Ben Marwick [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0001-7879-4531 ), David N. Matzig [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0001-7349-5401)   , Felix Riede [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0002-4879-7157), (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.17605/OSF.IO/RBQA5>

@@

  - [:file\_folder: paper](/analysis/paper): Quarto source document
    for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis. It also has a rendered version,
    `paper.docx`, suitable for reading (the code is replaced by figures
    and tables in this file)
  - [:file\_folder: data](/analysis/data): Data used in the analysis.
  - [:file\_folder: figures](/analysis/figures): Plots and other
    illustrations
